---
title: "main"
output: html_document
---

# Setup --------------------------------- 

```{r setup, echo=FALSE}
library(tidyverse)
library(janitor)
library(hrbrthemes)
library(ggridges)
library(ggrepel)
library(haven)
library(DataExplorer)
library(matlab)
library(quanteda)
library(tidytext)
library(tidymodels)

```

# Load data ----------------------------- 

```{r echo=FALSE, warning=FALSE, message=FALSE}
# Import data sources
charges <- read_csv("data/561118388_uncmedicalcenter_cdmstandardcharges.csv",
                name_repair = make_clean_names)

betos <- read_csv("~/unch-charges/data/betos.csv",
                name_repair = janitor::make_clean_names)

crosswalk <- read_csv("~/unch-charges/data/nc_crosswalk.csv",
                name_repair = janitor::make_clean_names)

hcpcs <- readxl::read_xlsx("~/unch-charges/data/HCPCS/HCPC2021_OCT_ANWEB.xlsx")
```


# Questions ---------------------------

1. What healthcare services vary most among payors? Do these have anything in common?
2. Most expensive services? Inexpensive?
3. How does Blue Cross Blue Shield compare to other commercial plans?
4. How do Medicare plans compare to others?
5. How does coverage vary across payors (proportion > $0.00)?
6. Which hospital room settings are most, least expensive?

# Preprocess ---------------------------

```{r preprocess}

# Remove unnecessary sub strings, pivot long, add medicare column, fix NA codes and add index
charges_clean <- charges %>%
  mutate(index_id = 1:nrow(.)) %>%
  select(-facility_name, -cash_discount) %>%
  mutate(code = str_remove(cpt_hcpcs, "MS-DRG: "), .keep = "unused") %>%
  mutate(clean_description = str_remove(charge_description, "HC "),
         .keep = "unused") %>%
  pivot_longer(
    cols = aetna:united_healthcare_medicare_advantage,
    names_to = "payor",
    values_to = "charge",
  ) %>%
  mutate(is.medicare = map_lgl(payor, ~ any(str_detect(., "medicare")) | (str_detect(., "humana")))) %>% # Note to lookup each for medicare
  mutate(across(payor, as_factor)) %>%
  mutate(code = replace_na(code, "NO CODE")) %>%
  mutate(index_long = 1:nrow(.)) %>%
  arrange(runif(nrow(.)))


# Remove $ and , from string, convert to numeric
charges_clean$price = as.double(gsub("[\\$,]", "", charges_clean$price))
charges_clean$min = as.double(gsub("[\\$,]", "", charges_clean$min))
charges_clean$max = as.double(gsub("[\\$,]", "", charges_clean$max))
charges_clean$charge = as.double(gsub("[\\$,]", "", charges_clean$charge))  

# regex for HC /^(?:HC )\b

payor_list <- charges_clean$payor %>% unique() %>% tibble() %>% arrange(desc(.));

```






```{r charge-variance}
charge_var <- charges_clean %>%
  select(payor, charge, code, clean_description, index_id) %>%
  group_by(code, clean_description, index_id) %>%
  summarise(max(charge), sd(charge), median(charge), mad(charge)) 

  # select(payor, charge, code) %>%
  # group_by(code) %>%
  # summarise(max_pay = max(charge),
  #           min_pay = min(charge)) 

# payor_var <- charges_wide %>%
#   rowwise() %>%
#   mutate(zscore = qnorm(
#     c_across(liberty_medicare_advantage:bcbs_unc_health_alliance)
#   )) %>%
#   ungroup() %>%
#   arrange(desc(zscore))


# payor_var <- charges_wide %>%
#   rowwise() %>%
#   mutate(zscore = (
#     avg = c_across(liberty_medicare_advantage:bcbs_unc_health_alliance) %>% mean()
#   ) / ((
#     dev = c_across(liberty_medicare_advantage:bcbs_unc_health_alliance) %>% sd()
#   ))) %>%
#     ungroup() %>%
#     arrange(desc(zscore))

# payor_var$'type' <- rownames(payor_var)
# 
# payor_var$type <-
#   ifelse(payor_var$zscore < 0, "below", "above")  # above / below avg flag
# 
# payor_var <- payor_var[order(payor_var$zscore),]  # sort
# 
# mtcars$`car name` <-
#   factor(mtcars$`car name`, levels = mtcars$`car name`)  # convert to factor to retain sorted order in plot.
# 
# ggplot(payor_var, aes(x=`car name`, y=mpg_z, label=mpg_z)) + 
#     # change default bar thickness from 1 to 0.5
#     # geom_bar() with stat=identity is geom_col
#     geom_col(aes(fill=mpg_type), width=.5)  +
#     #display mpg_z value for each bar in black
#     geom_text(color="black", size=3)+
#     scale_fill_manual(name="Mileage", 
#                     labels = c("Above Average", "Below Average"), 
#                     values = c("above"="green", "below"="tomato")) + 
#     labs(subtitle="Normalised mileage from 'mtcars'", 
#        title= "Diverging Bars") + 
#     #flip co-ordinate to show car names clearly/horizontally
#     coord_flip()



# payor_var <- charges_wide %>%
#   #select(-index_id,-code,-price,-min,-max,-clean_description) %>%
#   rowwise() %>%
#   mutate(variance = c_across(liberty_medicare_advantage:bcbs_unc_health_alliance) %>% var()) %>%
#   ungroup() %>%
#   arrange(desc(variance))
```




```{r outlier-detection}
# Widen data to look at payor data quality
charges_wide <- charges_clean %>%
  select(-is.medicare, everything()) %>%
  pivot_wider(
    id_cols=c("index_id","code", "price", "min", "max", "clean_description"),
    names_from = payor,
    values_from = charge,
#    names_glue = "{.value}_{payor}",
    values_fill = 0
  )

# ggplot(charges_wide, aes(x = charge_crescent)) +
#   geom_histogram(
#     binwidth = 200,
#     fill = "#69b3a2",
#     color = "#e9ecef",
#     alpha = 0.9
#   ) +
#   xlim(0, 2500)
# ggtitle("Bin size = 200") +
#   theme_ipsum() +
#   theme(plot.title = element_text(size = 15))

# outliers <- charges_clean %>%
#   group_by(payor) %>%
#   identify_outliers(charge)
# 
# charges_clean2 <- charges_clean %>% 
#   anti_join(outliers, by = "index_long") 

# Check descriptive stats on payors, remove skew lowest
# drop_payors <- charges_wide %>%
#   select(-price, -min, -max, -index_id) %>%
#   get_summary_stats(show = c("mean", "sd", "median", "iqr")) %>%
#   filter(median > 0)

```



```{r room-charges}
room_charge <- charges_wide %>% 
  filter(across(clean_description, ~ grepl('ROOM', .))) %>%
  distinct(clean_description, .keep_all = TRUE) %>%
  select(price, clean_description, index_id) %>%
  mutate(clean_description = factor(clean_description))
 
ggplot(room_charge, aes(reorder(clean_description, price), price)) +
  geom_col(aes()) +
  coord_flip() +
  labs(subtitle = "Hospital Room Cost by Type") +
  theme(
    panel.border = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.line = element_line(colour = "black")
  )
# alternative (after loading ggridges library)
# theme_ridges(grid = F, center_axis_labels = T)

```

```{r feat}
# Add features for range and price/charge difference
most_var <- charges_clean %>%
  filter(charge >= 1) %>%
  mutate(rng = max - min) %>%
  mutate(price_diff = charge - price)

most_var_h <- most_var %>%
  slice_max(price_diff, n = 20)

# Output data changes
# print(sprintf("Before simplification and deduplication: %d, after %d (%0.2f %% decrease)",
#               nrow(charges_clean),
#               nrow(charges_clean_ft),
#               100-100*nrow(charges_clean_ft)/nrow(charges_clean)));

# Recode NA codes
# charges_clean_ft2 <- charges_clean_ft %>%
#   mutate(code = replace_na(code, "NO CODE")) 

```


```{r charge-catagories}
category <- charges_clean %>%
  left_join(crosswalk, by = c("code" = "code"), keep = TRUE) %>%
  select(index_long, clean_description, description, index_id)

print(sprintf("Before inner join: %d, after %d (%0.2f %% decrease)",
              nrow(charges_clean),
              nrow(category),
              100-100*nrow(category)/nrow(charges_clean)));

cat_list <- category$description %>% unique() %>% tibble() %>% arrange(desc(.));

```



```{r crossref-catagories}
# betos_hcpcs <- hcpcs %>%
#   inner_join(betos, by = c("BETOS" = "permissible_value"), keep = TRUE)
# 
# betos_hcpcs <- clean_names(betos_hcpcs)
# 
# # unique_cat <- betos_hcpcs %>%
# #   group_by(domain_meaning_name) %>%
# #   distinct
# 
# betos_cat <- charges_clean %>%
#   inner_join(betos_hcpcs, by = c("code" = "hcpc"), keep = TRUE) %>%
#   select(clean_description, code, price, min, max, payor, charge, domain_meaning_name, long_description)
# 
# print(sprintf("Before simplification and join: %d, after %d (%0.2f %% decrease)",
#               nrow(betos_hcpcs),
#               nrow(charges_clean),
#               100-100*nrow(charges_clean)/nrow(betos_hcpcs)));
# charge_cat <- charges_long %>%
#   inner_join(betos_hcpcs, by = c("code" = "hcpc"), keep = TRUE) %>%
#   select(charge_description, code, price, min, max, payor, charge, domain_meaning_name, long_description)
# 
# charge_cat_leftjoin <- charges_long %>%
#   left_join(betos_hcpcs, by = c("code" = "hcpc"), keep = TRUE) %>%
#   select(charge_description, code, price, min, max, payor, charge, domain_meaning_name, long_description) %>%
#   mutate(is.medicare = map_lgl(payor, ~any(str_detect(., "medicare"))))
# 
# # All charges as 0 to 1 for matrices
# charge_cat[charge_cat == 0] <- 1

# Convert back to wide data
# charges_wide <- charges_long %>%
#                   select(-facility_name, -cpt_hcpcs) %>%
#                   pivot_wider(names_from = "payor",
#                     values_from = "charge",
#                     names_glue="{.value}_{payor}",
#                     values_fill=0) %>%
#                   mutate(index_cluster=1:nrow(.)) %>%
#                   arrange(runif(nrow(.)));

# charge_cat_wide <- charges_wide %>%
#     inner_join(betos_hcpcs, by = c("code" = "hcpc"), keep = TRUE) %>%
#     select(starts_with("charge_"), code, price, min, max, index_cluster, domain_meaning_name, long_description)
# 
# charge_cat_wide_qualitycheck <- charges_wide %>%
#     left_join(betos_hcpcs, by = c("code" = "hcpc"), keep = TRUE) %>%
#     select(starts_with("charge_"), code, price, min, max, index_cluster, permissible_value, domain_meaning_name, long_description)
# 
# charge_cat_wide[charge_cat_wide == 0] <- 1
  
```

```{r EXPERIMENT}
# test <- charges_long %>%
#   inner_join(crosswalk, by = c("cpt_hcpcs" = "code"), keep = TRUE) %>%
#   select(charge_description, code.x, price, min, max, payor, charge, description) %>%
#   mutate(is.medicare = map_lgl(payor, ~any(str_detect(., "medicare"))))

# test_wide <- test %>%
#   pivot_wider(names_from = "payor",
#               values_from = "charge",
#               names_glue="{.value}_{payor}",
#               values_fill=0) %>%
#   mutate(index_cluster=1:nrow(.)) %>%
#   arrange(runif(nrow(.))) %>%
#   select(!is_medicare)

# Changes is_medicare to TRUE
# test[test == 0] <- 1
# 
# test_wide[test_wide == 0] <- 1

```

```{r plots}

ggplot(test) +
  geom_bar(mapping = aes(x = fct_infreq(as.factor(description)))) +
  coord_flip() +
  labs(subtitle = "Quick Visualization")

ggplot(charges_clean) +
  geom_bar(mapping = aes(x = is.medicare)) +
  coord_flip() +
  labs(subtitle = "Quick Visualization")

```





```{r}
check <- charge_cat %>%
  group_by(payor) %>%
  summarise(avg = mean(charge, na.rm=TRUE)) %>%
  arrange(desc(avg)) %>%
  filter(quantile(avg, 0.5)<avg)

ggplot(check, aes(x = payor, y = avg)) +
    geom_col() +
    coord_flip()
```

```{r}
lm1 <- lm(test$charge ~ test$is.medicare + test$description)
summary(lm1)
```



```{r}


# Replace numerical NA with column mean
# charges_wide2 <-  for (i in which(sapply(charges_wide, is.numeric))) {
  #   charges_wide[is.na(charges_wide[, i]), i] <- mean(charges_wide[, i],  na.rm = TRUE)
  # }

```



```{r pca}
charges_matrix <- charges_wide %>%
  select(-clean_description, -code, -index_id, -price, -min, -max) %>%
  as.matrix();

library(missMDA)
# estimate number of components
nb <- estim_ncpPCA(charges_matrix, ncp.min=0, ncp.max=5)
# actual impute
charges_wide_impute <- imputePCA(charges_matrix, ncp=nb$ncp)

pca_fit <- prcomp(charges_wide_impute$completeObs);
  pca_fit$rotation
pca_fit$rotation

summary(pca_fit)

library(factoextra)

res.pca <- prcomp(charges_wide_impute$completeObs, scale = TRUE)

fviz_eig(res.pca)

fviz_pca_ind(res.pca,
             col.ind = "cos2", 
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
             repel = TRUE)
```


```{r scatterplot warning=FALSE}
# charges_long %>%
#   select(price, payor, charge) %>% 
  
ggplot(charges_long, aes(x = price, y = charge, label = payor)) + 
    geom_point(aes(), size = 1, alpha = 0.1) +
    # Highlight procedures > $75,000 in red
    geom_point(data = charges_long[charges_long$charge > 75000,], alpha = 0.5, color = "red", size = 2,) +
    # Only label procedures > $75,000 and avoid overlap
    geom_text_repel(data = charges_long[charges_long$charge > 75000,], 
      size = 2.5,
      nudge_x = .15,
      box.padding = 0.5,
      nudge_y = 1,
      segment.curvature = -0.1,
      segment.ncp = 3,
      segment.angle = 20
      ) +
    # Add Title, subtitle and axis labels
    labs(title = "Prices vs. Charges ",
      subtitle="UNC Medical Center, Aug 2021",
      x = "Price",
      y = "Charge", 
      caption = "Source | UNC Health") + 
    # Add theme from hrbrthemes lib
    theme_ipsum_rc() + 
    coord_cartesian(clip = "off")
```

```{r ridgeplot warning=FALSE, message=FALSE}
ggplot(charges_long, aes(x = charge, y = payor)) +
  geom_density_ridges(rel_min_height = 0) +
  scale_y_discrete(expand = c(0, 0)) +
  scale_x_continuous(limits = c(1, 1000), expand = c(0, 0.01)) +
  scale_fill_brewer(palette = 4) +
    labs(
        x = "Charge (USD)",
        y = "Payor",
        title = "Healthcare Insurance Comparison",
        subtitle = "Healthcare Services (n = 5011)",
        caption = "Source | UNC Health") + 
  theme_ridges() + theme(legend.position = "none")
```

```{r}
summary(charges_clean)
summary(charges_wide)
```


```{r}
charges_wide_matrix <- charges_wide %>%
  select_if(is.numeric) %>%
  select(!index_id) %>%
  arrange(desc(price), .by_group = TRUE) %>%
  as.matrix()
```


```{r}
heatmap(charges_wide_matrix, xlab="Payor", ylab="Charge Code", main="heatmap")
```


```{r}
p <- charges_clean %>%
  select(payor, charge, price, code) %>%
  filter(payor == "bcbs" | payor == "bcbs_medicare_advantage" | payor == "bcbs_unc_health_alliance" | payor == "blue_home") %>%
  mutate(across(payor, as_factor))

ggplot(p, aes(x=price, y=charge, color=payor)) + 
  geom_point()

ggplot(p, aes(charge)) + 
  geom_histogram(boundary = 0, bins = 20)
```

```{r lollipop }
ggplot(p, aes(x=payor, y=charge)) +
  geom_point() + 
  geom_segment( aes(x=payor, xend=1, y=0, yend=1000))
```


# Wrangle  ----------------------------


# Plot  -------------------------------
```{r medicare}
ggplot(charges_clean) +
  geom_bar(mapping = aes(x = is.medicare)) +
  coord_flip() +
  labs(subtitle = "Quick Visualization")
```





# Features  -------------------------------

```{r}
 # Scratch with 'test' data
# test2 <- charge_cat_leftjoin %>%
#   filter(charge > 0) %>%
#   mutate(rng = max - min) %>%
#   mutate(price_diff = charge - price)
# 
# 
# print(sprintf("Before simplification and deduplication: %d, after %d (%0.2f %% decrease)",
#               nrow(test),
#               nrow(test2),
#               100-100*nrow(test2)/nrow(test)));
#          

```



# Text analysis ---------------------------

```{r}
text <- charges_wide %>%
  unnest_tokens(word, clean_description)

print(sprintf("Before tokenizing: %d, after %d (%0.2f %% decrease)",
               nrow(charges_wide),
               nrow(text),
               100-100*nrow(text)/nrow(charges_wide)));

data(stop_words)

text2 <- text %>%
  anti_join(stop_words)

print(sprintf("Before removing stop words: %d, after %d (%0.2f %% decrease)",
               nrow(text),
               nrow(text2),
               100-100*nrow(text2)/nrow(text)));

nums <- text2 %>% filter(str_detect(word, "^[0-9]")) %>% select(word) %>% unique()

text2 <- text2 %>% 
  anti_join(nums, by = "word")

text2 %>%
  count(word, sort = TRUE) %>%
  filter(n > 50) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(n, word)) +
  geom_col() +
  labs(y = "Words from Charge Descriptions")

# text_bigrams <- charges_wide %>%
#   unnest_tokens(bigram, clean_description, token = "ngrams", n = 2)
# 
# bigrams_separated <- text_bigrams %>%
#   separate(bigram, c("word1", "word2"), sep = " ")
# 
# bigrams_filtered <- bigrams_separated %>%
#   filter(!word1 %in% stop_words$word) %>%
#   filter(!word2 %in% stop_words$word)
# 
# bigram_counts <- bigrams_filtered %>% 
#   count(word1, word2, sort = TRUE)
# 
# bigrams_united <- bigrams_filtered %>%
#   unite(bigram, word1, word2, sep = " ")
# 
# 
# AFINN <- get_sentiments("afinn")
# 
# not_words <- bigrams_separated %>%
#   filter(word1 == "not") %>%
#   inner_join(AFINN, by = c(word2 = "word")) %>%
#   count(word2, value, sort = TRUE)
# 
# not_words %>%
#   mutate(contribution = n * value) %>%
#   arrange(desc(abs(contribution))) %>%
#   head(20) %>%
#   mutate(word2 = reorder(word2, contribution)) %>%
#   ggplot(aes(n * value, word2, fill = n * value > 0)) +
#   geom_col(show.legend = FALSE) +
#   labs(x = "Sentiment value * number of occurrences",
#        y = "Words preceded by \"not\"")

```


# Utils --------------------------------------
```{r utils}



chars_to_factors <- function(df){
    for(n in names(df)){
        if(typeof(df[[n]]) == typeof('')){
            df[[n]] <- factor(df[[n]]);
        }
    }
    df;
}
```

```{r}

```

